---
title: "Salesforce - Boilerplate Code & Data Dictionary"
author: "Michael Jensen"
output: html_notebook
---
# Libraries and Data Sources

```{r}
library(magrittr)
library(odbc)
library(tidyverse)

odbc_sf  <- dbConnect(odbc::odbc(), "Salesforce")
```

# Database Tables

## Account Table

### Fields:

* Id (string):
* IsDeleted (boolean):
* MasterRecordId (string):
* Name (string): The name of the entity.
  * Filter out `test city 2`.
* Type (string):
* RecordTypeId (string): The Record Type ID (foreign key for RecordType.Id).
* ParentId (string):
* BillingStreet (string):
* BillingCity (string):
* BillingState (string):
* BillingPostalCode (string):
* BillingCountry (string):
* BillingLatitude (double):
* BillingLongitude (double):
* BillingGeocodeAccuracy (string):
* BillingAddress (string):
*
*
*
* 
* 
*
*
*
*
* Phone (string):
* Fax (string):

### Code

```{r}
Account_governments <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      a.Id   AS entity_id,
      a.Name AS entity_name,
      r.Name AS govt_type
    FROM Account         AS a
    LEFT JOIN RecordType AS r
    ON a.RecordTypeId = r.Id
    WHERE a.RecordTypeId IN (
      SELECT Id
      FROM RecordType
      WHERE SobjectType = 'Account'
      AND IsActive = 'TRUE'
      AND Name NOT IN (
        'Community User',
        'Court (Search Under Parent Entity)',
        'CPA Firm',
        'Health Provider',
        'Non Profits'))
    AND a.Name <> 'test city 2'") %>% 
  as_tibble()

Account_local_governments <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      a.Id   AS entity_id,
      a.Name AS entity_name,
      r.Name AS govt_type
    FROM Account         AS a
    LEFT JOIN RecordType AS r
    ON a.RecordTypeId = r.Id
    WHERE a.RecordTypeId IN (
      SELECT Id
      FROM RecordType
      WHERE SobjectType = 'Account'
      AND IsActive = 'TRUE'
      AND Name NOT IN (
        'Community User',
        'Court (Search Under Parent Entity)',
        'CPA Firm',
        'Health Provider',
        'Independent/Quasi State Entity',
        'Institution of Higher Education',
        'Non Profits',
        'State of Utah (agencies/depts/comp units/ etc.)'))
    AND a.Name <> 'test city 2'") %>% 
  as_tibble()
```

## RecordType Table

### Fields:

* Id (string): Record Type ID (primary key).
* Name (string): The name of the record type.
* DeveloperName (string): The name of the record type, with underscores instead of spaces between words.
* Namespace Prefix (string): NA field.
* Description (string): Description of the record type.
  * Mostly `NA` values.
* BusinessProcessId (string):
* SobjectType (string): 
  * State and local government records have an `SobjectType` value of `Account`, though not all `Account` records are state or local governments.
* IsActive (boolean): Whether the record type is active.
* CreatedById (string):
* CreatedDate (datetime:
* LastModifiedById (string):
* LastModifiedDate (datetime):
* SystemModstamp (datetime):

### Code

```{r}
RecordType_governments <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      Id          AS record_type_id, 
      Name        AS record_type_name, 
      Description AS description
    FROM RecordType
    WHERE SobjectType = 'Account'
    AND IsActive = 'TRUE'
    AND Name NOT IN (
      'Community User',
      'Court (Search Under Parent Entity)',
      'CPA Firm',
      'Health Provider',
      'Non Profits')")

RecordType_local_governments <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      Id          AS record_type_id, 
      Name        AS record_type_name, 
      Description AS description
    FROM RecordType
    WHERE SobjectType = 'Account'
    AND IsActive = 'TRUE'
    AND Name NOT IN (
      'Community User',
      'Court (Search Under Parent Entity)',
      'CPA Firm',
      'Health Provider',
      'Independent/Quasi State Entity',
      'Institution of Higher Education',
      'Non Profits',
      'State of Utah (agencies/depts/comp units/ etc.)')")  
```

## Report_Review__c Table

```{r}
report_review__c_2018 <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      a.Name                            AS entity_name,
      y.Name                            AS report_year,
      t.Name                            AS record_type,
      r.Total_Revenue_or_Expenditure__c AS total_rev_or_exp,
      r.Total_Expenditure__c            AS total_exp,
      r.Total_Revenue__c                AS total_rev
    FROM Report_Review__c               AS r
    LEFT JOIN Account                   AS a
    ON r.Entity_Name__c = a.Id
    LEFT JOIN RecordType                AS t
    ON r.RecordTypeID = t.Id
    LEFT JOIN Report_Year__c            AS y
    ON r.review_report_year__c = y.Id
    WHERE t.Name IN (
      'AUP Checklist',
      'Large Entity Checklist',
      'LEA Checklist',
      'Small Entity Checklist')
    AND r.review_report_year__c IN (
      SELECT Id
      FROM Report_Year__c
      WHERE Name = '2018')") %>% 
  mutate(total = 
           if_else(
             !is.na(total_rev_or_exp), 
             total_rev_or_exp,
             if_else(
               total_exp > total_rev,
               total_exp,
               total_rev)))
```

## Transparency_Reporting_c Table

```{r}
transparency_reporting__c <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      IsDeleted        AS is_deleted,
      Name             AS report_date_name,
      CreatedDate      AS created_date,
      CreatedById      AS created_by,
      LastModifiedDate AS last_modified_date,
      LastModifiedById AS last_modified_by,
      Account__c       AS entity_id,
      Status__c        AS transparency_status,
      Id               AS id
    FROM Transparency_Reporting__c") %>% 
  left_join(entity_names, by = "entity_id") %>% 
  left_join(user_names,   by = c("created_by" = "user_id")) %>% 
  left_join(user_names,   by = c("created_by" = "user_id")) %>% 
  rename(created_by_name       = user_name.x,
         last_modified_by_name = user_name.y) %>% 
  select(report_date_name, entity_name, transparency_status, created_date,
         created_by_name, last_modified_date, last_modified_by_name, is_deleted,
         entity_id, created_by, last_modified_by, id)
```

## Transparency_Reporting__c_hd Table

```{r}
transparency_reporting__c_hd <- 
  dbGetQuery(
    odbc_sf,
    "SELECT 
      ParentId AS parent_id,
      IsDeleted AS is_deleted,
      ValidFromDate AS valid_from_date,
      CreatedDate AS created_date,
      CreatedById AS created_by,
      Status__c_hpr,
      Status__c_hst
    FROM Transparency_Reporting__c_hd") %>% 
  left_join(user_names, by = c("created_by" = "user_id"))
```

## User Names

```{r}
user_names <- 
  dbGetQuery(
    odbc_sf,
    "SELECT
      Id   AS user_id,
      Name AS user_name
    FROM User")
```

# DBMS Disconnection

```{r}
dbDisconnect(odbc_sf)
```

# Workspace
