---
title: "Compare LG & OSA Entity Lists"
author: "Michael Jensen"
output: html_notebook
---
# Program Description

**Purpose**

Compare the Lt. Governor's Local Government Registry with OSA's list of entities to identify entities that appear on one list and not the other.

See https://entityregistry.utah.gov/ for more information on the LG's Office entity registration requirements.

**Input(s)**

* The DSN to Salesforce.
* The LG Registry file titled "Entity Registry Tentative Data_9-13-19.csv."

```{r}
dsn_sf  <- "Salesforce"

LG <- 
  list(
    registry_raw = 
      readr::read_csv(
    "C:/Users/mjensen1/Documents/3 Project Support/Salesforce/Entity Registry Tentative Data_9-13-19.csv"))
```

**Output(s)**

* A .csv file containing the names of entities that are on the LG Registry and not in Salesforce.
* A .csv file containing the names of entities that are in Salesforce and not on the LG Registry.
* A report of any notable information I become aware of as I work with the LG Registry.

```{r}
reports <- 
  list(
    lg_not_in_osa = list(),
    osa_not_in_lg = list(),
    notable_info  = list())
```

# Libraries and Data Sources

```{r}
library(fuzzyjoin)
library(odbc)
library(splitstackshape)
library(rJava)
library(qdap)
library(tidyverse)

odbc_sf <- dbConnect(odbc::odbc(), dsn_sf)
rm(dsn_sf)
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}

```

# Execution

## Import OSA Entities

Import limited purpose and local government entities from Salesforce (the entity types required to register with the LG's Office):

```{r}
OSA <- 
  list(
    entities_raw = 
      dbGetQuery(
        odbc_sf,
        "SELECT 
          a.Name AS entity_name,
          r.Name AS osa_govt_type
        FROM Account         AS a
        LEFT JOIN RecordType AS r
        ON a.RecordTypeId = r.Id
        WHERE a.RecordTypeId IN (
          SELECT Id
          FROM RecordType
          WHERE SobjectType = 'Account'
          AND IsActive = 'TRUE'
          AND Name NOT IN (
            'Community User',
            'Court (Search Under Parent Entity)',
            'CPA Firm',
            'Health Provider',
            'Institution of Higher Education',
            'State of Utah (agencies/depts/comp units/ etc.)'))
        AND a.Name <> 'test city 2'
        AND Entity_Status__c NOT IN ('Inactive', 'Dissolved')") %>% 
      as_tibble())
```

## Tidy

```{r}
dictionary_osa_entity_names <- 
  cSplit(OSA$entities_raw, "entity_name", sep = " ") %>% 
  distinct()

d <- 
  OSA$entities_raw %>% 
  select(entity_name) %>% 
  cSplit(., "entity_name", sep = " ") %>% 
  collapse()

# How can I get a single vector, to use as a second dictionary?
e <- 
  d %>% 
  unite(testnames)

e <- 
 d %>% 
  as_vector()

f <- 
  e[[]]
  

class(OSA$entities_raw)

spelling <- 
  check_spelling(OSA$entities_tidying$entity_name)
  
```

```{r}
LG$registry_tidying <- 
  LG$registry_raw %>% 
  rename(
    lg_govt_type = `Entity Type`,
    entity_name  = `Entity Name`,
    lg_county       = `County`) %>% 
  mutate(
    entity_name = str_replace(entity_name, " - ", " – "),
    entity_name = str_replace(entity_name, " — ", " – " ),
    entity_name = str_replace(entity_name, "Dsitrict", "District"))

reports$notable_info$lg_invalid_names <- 
  LG$registry_tidying %>% 
  filter(entity_name %in% c("Test", ",mnn"))

LG$registry_tidying <-
  LG$registry_tidying %>%
  filter(!entity_name %in% c("Test", ",mnn")) %>%
  map_if(is.character, str_to_title) %>% 
  bind_rows() %>% 
  mutate(duplicate_record = duplicated(.))

reports$notable_info$duplicate_record <- 
  LG$registry_tidying %>% 
  filter(duplicate_record) %>% 
  arrange(entity_name)

LG$registry_tidying <- 
  LG$registry_tidying %>% 
  filter(!duplicate_record) %>% 
  select(entity_name, lg_govt_type, lg_county) %>% 
  mutate(duplicate_name_type_county = duplicated(.))

reports$notable_info$duplicate_name_type_county <- 
  LG$registry_tidying %>% 
  filter(duplicate_name_type_county) %>% 
  select(-duplicate_name_type_county) %>% 
  arrange(entity_name)

LG$registry_tidying <- 
  LG$registry_tidying %>% 
  filter(!duplicate_name_type_county) %>% 
  select(-duplicate_name_type_county)

LG$registry_tidy <- 
  LG$registry_tidying
```

```{r}
a <- check_spelling(LG$registry_raw$`Entity Name`)
```



```{r}
OSA$entities_tidying <- 
  OSA$entities_raw %>% 
  mutate(
    entity_name = str_to_title(entity_name),
    duplicate_record = duplicated(.),
    duplicate_name   = duplicated(.$entity_name))

if (OSA$entities_tidying %>% filter(duplicate_record) %>% nrow() > 0) {
  
  stop("Duplicate records found in OSA data. Correct in Salesforce and reimport")
}

if (OSA$entities_tidying %>% filter(duplicate_name) %>% nrow() > 0) {
  
  stop("Duplicate entity names found in OSA data. Correct in Salesforce and reimport")
}

OSA$entities_tidying <- 
  OSA$entities_tidying %>% 
  select(entity_name, osa_govt_type)

OSA$entities_tidy <- 
  OSA$entities_tidying
```

## Transform

### Create Standard Government Types

```{r}
LG$registry_tidy <- 
  LG$registry_tidy %>% 
  mutate(
    common_govt_type = 
      case_when(
        str_detect(lg_govt_type, regex("^Area Agency")) ~ "Area Agency",
        lg_govt_type %in% c("Charter School", "School District") ~ "LEA",
        lg_govt_type == "Community Reinvestment Agency" ~ "CRA",
        lg_govt_type == "Conservation District" ~ "Conservation District",
        lg_govt_type == "County" ~ "County",
        lg_govt_type == "Housing Authority" ~ "Housing",
        lg_govt_type == "Municipality" ~ "Municipality",
        str_detect(lg_govt_type, regex("Nonprofit")) ~ "Non Profit",
        lg_govt_type == 
          "Independent Entity or Independent State Agency" ~ 
          "Independent Agency",
        lg_govt_type %in% 
          c("Interlocal Entity", "Substance Abuse Authority") ~ 
          "AOG or Interlocal",
        lg_govt_type == "Local Building Authority" ~ "Local Building Authority",
        lg_govt_type %in% 
          c("Local District", "Special Service District") ~ "Local or SSD",
        lg_govt_type == "Local Health Department" ~ "Health Department",
        lg_govt_type == "Local Mental Health Authority" ~ "Mental Health",
        str_detect(entity_name, "Circle The Wagons Inc.") ~ "Non Profit",
        str_detect(entity_name, "City Of Moab Redevelopment Agency") ~ "CRA",
        str_detect(entity_name, "Marysvale Town") ~ "Municipality",
        str_detect(entity_name, "Marysvale Town Local Building Authority") ~ 
          "Local Building Authority",
        str_detect(entity_name, "Perry City Redevelopment Agency") ~ "CRA",
        str_detect(entity_name, "Pleasant View City Redevelopment Agency") ~ 
          "CRA",
        str_detect(
          entity_name, 
          "Price City Urban Renewal And Community Development Agency") ~ "CRA",
        str_detect(entity_name, "Virgin Town") ~ "Municipality",
        str_detect(entity_name, "Weber Human Services") ~ "AOG or Interlocal",
        str_detect(entity_name, "Wellington City Redevelopment Agency") ~ "CRA"))
```

```{r}
lg_data$entities <- 
  lg_data$entities %>% 
  mutate(govt_type = case_when(
           str_detect(lg_govt_type, regex("^Area Agency")) ~ "Area Agency",
           lg_govt_type %in% c("Charter School", "School District") ~ "LEA",
           lg_govt_type == "Community Reinvestment Agency" ~ "CRA",
           lg_govt_type == "Conservation District" ~ "Conservation District",
           lg_govt_type == "County" ~ "County",
           lg_govt_type == "Housing Authority" ~ "Housing",
           lg_govt_type == "Municipality" ~ "Municipality",
           str_detect(lg_govt_type, regex("Nonprofit")) ~ "Non Profit",
           lg_govt_type == 
             "Independent Entity or Independent State Agency" ~ 
             "Independent Agency",
           lg_govt_type %in% 
             c("Interlocal Entity", "Substance Abuse Authority") ~ 
             "AOG or Interlocal",
           lg_govt_type == "Local Building Authority" ~ 
             "Local Building Authority",
           lg_govt_type %in% 
             c("Local District", "Special Service District") ~ "Local or SSD",
           lg_govt_type == "Local Health Department" ~ "Health Department",
           lg_govt_type == "Local Mental Health Authority" ~ "Mental Health",
           str_detect(entity_name, "Circle The Wagons Inc.") ~ "Non Profit",
           str_detect(entity_name, "City Of Moab Redevelopment Agency") ~ "CRA",
           str_detect(entity_name, "Marysvale Town") ~ "Municipality",
           str_detect(entity_name, "Marysvale Town Local Building Authority") ~ 
             "Local Building Authority",
           str_detect(entity_name, "Perry City Redevelopment Agency") ~ "CRA",
           str_detect(entity_name, "Pleasant View City Redevelopment Agency") ~
             "CRA",
           str_detect(
             entity_name, 
             "Price City Urban Renewal And Community Development Agency") ~
             "CRA",
           str_detect(entity_name, "Virgin Town") ~ "Municipality",
           str_detect(entity_name, "Weber Human Services") ~ 
             "AOG or Interlocal",
           str_detect(entity_name, "Wellington City Redevelopment Agency") ~
             "CRA"))

sf_data$entities <- 
  sf_data$entities %>% 
  mutate(govt_type = case_when(
           sf_govt_type %in% c("AOG", "Interlocal") ~ "AOG or Interlocal",
           sf_govt_type %in% c("City", "Town") ~ "Municipality",
           sf_govt_type %in% 
            c("Community_Reinvestment_Agency", 
              "Redevelopment_Agency_Project_Area") ~ "CRA",
           sf_govt_type == "Conservation_District" ~ "Conservation District",
           sf_govt_type == "County" ~ "County",
           sf_govt_type == "Housing" ~ "Housing",
           sf_govt_type %in% 
            c("Independent_Quasi_State_Entity", "State_Agency") ~ 
             "Independent Agency",
           sf_govt_type == "District_Health" ~ "Health Department",
           sf_govt_type == "Institute_of_Higher_Education" ~ "Higher Education",
           sf_govt_type == "Justice_Court" ~ "Other",
           sf_govt_type == "Local_and_Special_Service_District" ~ 
             "Local or SSD",
           sf_govt_type == "Mental_Health" ~ "Mental Health",
           sf_govt_type == "Non_Profits" ~ "Non Profit",
           sf_govt_type == "School_District_or_Charter_School" ~ "LEA"))
```

## Learn `fuzzyjoin::stringdist_join()`

### Sample data:

```{r, eval=FALSE}
table_a <- 
  tibble(
    entity_name = c("City of Cedar Hills", "Bluff"))

table_b <- 
  tibble(
    entity_name = c("Cedar Hills", "Bluff City"))
```

### Levenshtein Distance (`method = 'lv'`)

```{r, eval=FALSE}
# max_dist = 2 (the default) won't match the tables:
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  method = "lv",
  mode = "left",
  distance_col = "lv_dist")

# max_dist = 5 will match Bluff, but not Cedar Hills:
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  max_dist = 5,
  method = "lv",
  mode = "left",
  distance_col = "lv_dist")

# max_dist = 8 is required to get "City of Cedar Hills" to match "Cedar Hills:"
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  max_dist = 8,
  method = "lv",
  mode = "left",
  distance_col = "lv_dist")

# max_dist = 8 allows "Alpine City" to pair with "Green Party:"
lg_sf_left_lv <- 
  stringdist_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    max_dist = 8,
    method = "lv",
    mode = "left",
    distance_col = "lv_dist")

rm(lg_sf_left_lv)
```

Conclusion: Levenshtein distance is not helpful.

### Optimal String Alignment Distance (`method = 'osa'`)

```{r, eval=FALSE}
# max_dist = 5 will match Bluff, but not Cedar Hills:
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  max_dist = 5,
  method = "osa",
  mode = "left",
  distance_col = "lv_dist")

# max_dist = 8 is required to get "City of Cedar Hills" to match "Cedar Hills:"
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  max_dist = 8,
  method = "osa",
  mode = "left",
  distance_col = "lv_dist")

# max_dist = 8 allows "Alpine City" to pair with "Green Party:"
lg_sf_left_osa <- 
  stringdist_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    max_dist = 8,
    method = "osa",
    mode = "left",
    distance_col = "lv_dist")

rm(lg_sf_left_osa)
```

Conclusion: Same conclusion as using Levenshtein (which makes sense, as the two methods are similar). Not helpful here.

### Longest Common Substring (`method = 'lcs'`)

```{r, eval=FALSE}
# max_dist = 5 will match Bluff, but not Cedar Hills:
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  max_dist = 5,
  method = "lcs",
  mode = "left",
  distance_col = "lcs_distance")

# max_dist = 8 is required to get "City of Cedar Hills" to match "Cedar Hills:"
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  max_dist = 8,
  method = "lcs",
  distance_col = "lcs_distance")

# max_dist = 8 won't pair "Alpine City" with "Green Party," so that's an 
# improvement from the methods above.
lg_sf_left_lcs <- 
  stringdist_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    max_dist = 8,
    method = "lcs",
    mode = "left",
  distance_col = "lcs_distance")

rm(lg_sf_left_lcs)
```

Conclusion: For our purposes, better than the Levenshtein and OSA methods.

### Jaccard Distance (`method = 'jaccard'`)

The Jaccard Distance method returns the Cartesian product of the inputs.

A Jaccard Distance of 0 indicates no match, and a Jaccard Distance of 1 indicates a perfect match.

```{r, eval=FALSE}
# This method gives a higher match for the pairings that make the least sense:
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  method = "jaccard",
  mode = "left",
  distance_col = "jaccard_distance")
```

Conclusion: Not a good method to use here.

### Jaro Distance (`method = 'jw', p = 0`)

The Jaro Distance method returns the Cartesian product of the inputs.

A Jaro Distance of 0 indicates a complete match, while a distance of 1 indicates complete dissimilarity.

Modifying the value of `p` changes the Jaro Distance to the Jaro-Winkler Distance. Given how the Jaro-Winkler Distance calculates the `l` value, I don't see a reason to explore that method.

```{r, eval=FALSE}
stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  method = "jw",
  p = 0,
  mode = "left",
  distance_col = "jw_distance")

lg_sf_left_jw <- 
  stringdist_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    method = "jw",
    p = 0,
    mode = "left",
  distance_col = "jw_distance")

rm(lg_sf_left_jw)
```

Conclusion: This seems to be the best method so far, though I'll need to filter the data in order to get back to only one observation per entity.

## Analysis

### Summarize Differences, by Gov't Type

```{r}
lg_vs_sf <- 
  list(
    sf_type_not_in_lg = 
      sf_data$entities %>% 
      distinct(govt_type) %>% 
      anti_join(
        lg_data$entities %>% distinct(govt_type),
        by = "govt_type"),
    
    lg_type_not_in_sf = 
      lg_data$entities %>% 
      distinct(govt_type) %>% 
      anti_join(
        sf_data$entities %>% distinct(govt_type),
        by = "govt_type"),
    
    type_totals =
      full_join(
        sf_data$entities %>% 
          group_by(govt_type) %>% 
          summarize(sf_total = n()),
        lg_data$entities %>% 
          group_by(govt_type) %>% 
          summarize(lg_total = n()),
        by = "govt_type") %>% 
      mutate(sf_total = if_else(is.na(sf_total), 0L, sf_total),
             lg_total = if_else(is.na(lg_total), 0L, lg_total),
             difference = abs(sf_total - lg_total)) %>% 
      arrange(desc(difference))
)
```

### Report: Differences

```{r}
any(
  lg_data$entities %>% 
    filter(govt_type == "Local Building Authority") %>% 
    select(entity_name)
  %in% 
  sf_data$entities$entity_name)

any(
  lg_data$entities %>% 
    filter(govt_type == "Area Agency") %>% 
    select(entity_name)
  %in% 
  sf_data$entities$entity_name)

any(
  sf_data$entities %>% 
    filter(govt_type == "Higher Education") %>% 
    select(entity_name)
  %in% 
  lg_data$entities$entity_name)
```

```{r}
lg_vs_sf$lg_is_missing <- 
  sf_data$entities %>% 
  filter(govt_type == "Higher Education")

lg_vs_sf$sf_is_missing <- 
  lg_data$entities %>% 
  filter(govt_type %in% c("Local Building Authority", "Area Agency"))
```

### Jaro Distance

```{r}




lg_sf_left_jaro <- 
  stringdist_join(
    lg_data$entities,
    sf_data$entities,
    by = "entity_name"
  )


stringdist_join(
  table_a,
  table_b,
  by = "entity_name",
  method = "jw",
  p = 0,
  mode = "left",
  distance_col = "jw_distance")

lg_sf_left_jw <- 
  stringdist_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    method = "jw",
    p = 0,
    mode = "left",
  distance_col = "jw_distance")

rm(lg_sf_left_jw)
```


```{r}
lg_sf_left <- 
  stringdist_join(
    lg_data$entities,
    sf_entities,
    by = "entity_name",
    method = "jw",
    p = 0,
    mode = "left",
  distance_col = "jw_distance")

lg_sf_anti <- 
  stringdist_join(
    lg_data$entities,
    sf_entities,
    by = "entity_name",
    method = "jw",
    p = 0,
    mode = "anti",
  distance_col = "jw_distance")

```

Fuzzy join:

```{r}
lg_entities <- 
  lg_entities %>% select(entity_name)

sf_entities <- 
  sf_entities %>% select(entity_name)

join_lg_sf_left <- 
  stringdist_left_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    method = "jaccard",
    distance_col = "jaccard_distance") %>% 
  arrange(entity_name.x, desc(jaccard_distance))

join_lg_sf_left2 <- 
  stringdist_left_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    method = "jw", p = 0,
    distance_col = "jaro_distance") %>% 
  arrange(entity_name.x, desc(jaro_distance))

join_lg_sf_left3 <- 
  stringdist_left_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    method = "lv",
    distance_col = "lv_distance") %>% 
  arrange(entity_name.x, desc(lv_distance))

join_lg_sf_anti <- 
  stringdist_anti_join(
    lg_entities,
    sf_entities)

match_anti_lg <- 
  stringdist_anti_join(
    lg_entities,
    sf_entities,
    by = "entity_name",
    max_dist = 4)

match_anti_osa <- 
  stringdist_anti_join(
    sf_entities,
    lg_entities,
    by = "entity_name")
  
match_left_lg <- 
  stringdist_left_join(
    lg_entities,
    sf_entities,
    by = "entity_name") %>% 
  select(
    lg_name  = entity_name.x,
    osa_name = entity_name.y,
    lg_type  = entity_type.x,
    osa_type = entity_type.y)
```

## Report: On LG Registry and not in Salesforce

## Report: In Salesforce and not on LG Registry


## Report: Notable Information

"Entity Registry Tentative Data_9-13-19.csv" contains:

* On initial import, 1707 observations of 38 variables.
  * Two test entities, both with an `Entity Name` value of "Test."
  * One entity named ",mnn."
  * Ten observations that are exact duplicates of at least one other observation (across all variables).
  * 97 `Entity Name` values that are a duplicate of another `Entity Name` value (some of these appear to be valid).
  * `Entity Type` values that are `NA`, `Not Sure`, duplicated (e.g., two types of "Area Agency"), incorrect for the entity (e.g., Clearfield Housing Authority is listed as a Municipality), and that do not match the government types we use at OSA (why do two State agencies have different lists of the possible government types?).

* After removing the two test entities, the entity named ",mnn.," and the eight observations that are exact duplicates of another observation, the LG Registry contains 1696 entities. OSA has 1667 entities, which is a total difference of 29.

# DBMS Disconnection

```{r}
dbDisconnect(odbc_sf)
```